% !TEX root = ../paper.tex

\begin{itemize}
  \item M-matrix
  \item positivity preservation
  \item local DMP
\end{itemize}

The role of a low-order scheme in the context of the FCT algorithm is to
provide a fail-safe solution, which has desirable properties such as
positivity-preservation and lack of spurious oscillations. These properties
come at the cost of excessive artificial diffusion and thus a lesser degree
of accuracy. However, the idea of the FCT algorithm is to undo this disadvantage
as much as possible without violating some physically-motivated solution bounds.

Here positivity-preservation and monotonicity are achieved by satisfying
the M-matrix property of the matrix inverted in the low-order system.
M-matrices are a subset of inverse-positive matrices and have the monotone
property; for the linear system $\A\x = \ssrhs$, an M-matrix $\A$ has the property
\begin{equation}
  \ssrhs \geq 0 \quad \Rightarrow \quad \x \geq 0 \eqp
\end{equation}
Thus proving positivity-preservation, given the linear system matrix is an
M-matrix, is achieved by proving positivity of the right-hand-side vector $\ssrhs$.
This monotonicity property of the linear system matrix is also responsible for
the lack of spurious oscillations.

In this section, the first-order viscosity method introduced by Guermond
\cite{guermond_firstorder} will be adapted to the model equation given by
Equation \eqref{eq:scalar_model}. This method uses an element-wise artificial
viscosity definition in conjunction with a graph-theoretic local viscous
bilinear form that makes the method valid for arbitrary element shapes and
dimensions. These definitions will be shown to ensure that the system matrix
is a non-singular M-matrix.

The graph-theoretic local viscous bilinear form has the following definition.
%-------------------------------------------------------------------------------
\begin{defn}[Local Viscous Bilinear Form]
   The local viscous bilinear form for element $K$ is defined as follows:
   \begin{equation}\label{eq:bilinearform}
     d_K(\test_j,\test_i) \equiv \left\{\begin{array}{l l}
       -\frac{1}{n_K - 1}V_K & i\ne j\eqc \quad i,j\in \indices_K\eqc \\
       V_K                   & i = j \eqc \quad i,j\in \indices_K\eqc \\
       0                     & \mbox{otherwise}\eqc
     \end{array}\right.
   \end{equation}
   where $V_K$ is the volume of cell $K$, $\indices_K$ is the set of degree
   of freedom indices such that the corresponding test function has support
   on cell $K$, and $n_K$ is the number of indices in that set.
\end{defn}
%-------------------------------------------------------------------------------
This bilinear form bears resemblance to a standard Laplacian bilinear form:
the diagonal entries are positive, the off-diagonal entries are negative, and
the row sums are zero. These facts will be invoked in the proof of the M-matrix
conditions later in this section.

The element-wise viscosity definition from \cite{guermond_firstorder} is
adapted to account for the reaction term in Equation \eqref{eq:scalar_model}
but otherwise remains unchanged.
%-------------------------------------------------------------------------------
\begin{defn}[Low-Order Viscosity]
  The low-order viscosity for cell $K$ is defined as follows:
  \begin{equation}
    \nu^L_K \equiv \max\limits_{i\ne j\in\indices_K}
      \frac{\max(0,A_{i,j})}
      {-\sum\limits_{T\subset S_{i,j}}d_T(\test_j,\test_i)}
      \eqc
  \end{equation}
  where $A_{i,j}$ is the $i,j$th entry of the Galerkin steady-state matrix
  given by Equation \eqref{eq:Aij}.
\end{defn}
%-------------------------------------------------------------------------------
This viscosity definition is designed to give the minimum amount of artificial
diffusion without violating the M-matrix conditions.

Now the low-order system will be described.
Consider a modification of the Galerkin scheme given in Equation \eqref{eq:galerkin_semidiscrete}
which lumps the mass matrix ($\M^C \rightarrow \M^L$) and adds an artificial
diffusion operator $\D^L$, called the low-order diffusion matrix:
\begin{equation}
  \M^L\ddt{\U^L} + (\A + \D^L)\U(t) = \ssrhs(t) \eqc
\end{equation}
where $\U^L(t)$ denotes the discrete low-order solution values. The low-order
diffusion matrix is assembled element-wise using the local viscous bilinear
form and low-order viscosity definitions:
\begin{equation}\label{eq:low_order_diffusion_matrix}
  D_{i,j}^L \equiv
    \sum\limits_{K\subset S_{i,j}}\nu^L_K
    d_K(\test_j,\test_i) \eqp
\end{equation}

Now the low-order scheme has been fully described, and some statements will be
made on its properties. Firstly the M-matrix property will be claimed for
the matrix $\A^L\equiv\A + \D^L$, which will hereafter be referred to as the
low-order steady-state system matrix.
%-------------------------------------------------------------------------------
\begin{thm}[M-matrix property]
  The low-order steady-state system matrix $\A^L$ is a non-singular M-matrix.
\end{thm}
\input{content/m_matrix}
%-------------------------------------------------------------------------------
