\documentclass[12pt]{article}
\usepackage[letterpaper]{geometry}
\geometry{verbose,tmargin=1in,bmargin=1in,lmargin=1in,rmargin=1in}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{booktabs} % for different rule commands such as \toprule
\usepackage{graphicx} % for including graphics
\usepackage{subcaption}
\usepackage[hidelinks]{hyperref}

% create path commands
\newcommand{\refdir}{../dissertation}
\newcommand{\contentdir}{../dissertation/content}

% input user-defined commands
\input{\contentdir/newcommands}
\input{\contentdir/theorems_dissertation}

%###############################################################################
% Document
%###############################################################################
\begin{document}

\begin{center}
  {\large
    Application of the Entropy Viscosity Method and the Flux-Corrected Transport
    Algorithm to Scalar Transport Equations and the Shallow Water Equations
  }

  {\scriptsize
    Dissertation Proposal
  }

  \vspace{1em}

  Joshua E. Hansel
\end{center}

%###############################################################################
\section{Introduction}
%###############################################################################
\input{\contentdir/introduction/purpose}

The organization of this proposal is as follows.
Section \ref{sec:problem_formulation} gives and discusses the physical models,
problem formulation, and discretization.
Section \ref{sec:methodology} discusses the methodology used, including
entropy-based artificial dissipation and the flux-corrected transport
algorithm.
Section \ref{sec:results} gives a sample of preliminary results.
Section \ref{sec:goals} discusses the goals of this research.
Section \ref{sec:conclusions} gives a summary and conclusions of this proposal.

%###############################################################################
\section{Problem Formulation\label{sec:problem_formulation}}
%###############################################################################
%===============================================================================
\subsection{Physical Models}
%===============================================================================
This section introduces the PDEs under consideration. Section
\ref{sec:scalar_model} introduces the scalar hyperbolic PDE model, and
Section \ref{sec:sw_model} introduces the shallow water equations.
%-------------------------------------------------------------------------------
\subsubsection{Scalar Transport\label{sec:scalar_model}}
%-------------------------------------------------------------------------------
\input{\contentdir/preliminaries/scalar}
%-------------------------------------------------------------------------------
\subsubsection{The Shallow Water Equations\label{sec:sw_model}}
%-------------------------------------------------------------------------------
\input{\contentdir/preliminaries/shallowwater}

%===============================================================================
\subsection{Discretization}
%===============================================================================
This section gives the spatial and temporal discretizations. Section
\ref{sec:spatial_discretization_scalar} gives the spatial discretization
for the scalar model given in Section \ref{sec:scalar_model}, and
Section \ref{sec:spatial_discretization_sw} gives the spatial discretization
for the shallow water equations, introduced in Section \ref{sec:sw_model}.
In both cases, the continuous Galerkin finite element method (FEM) is employed
with basis functions from a piecewise linear polynomial space.
Section \ref{sec:temporal_discretization} gives the temporal discretizations
used.

%-------------------------------------------------------------------------------
\subsubsection{Spatial Discretization of the Scalar Hyperbolic PDE Model
\label{sec:spatial_discretization_scalar}}
%-------------------------------------------------------------------------------
\input{spatial_discretization_scalar}

%-------------------------------------------------------------------------------
\subsubsection{Spatial Discretization of the Shallow Water Equations
\label{sec:spatial_discretization_sw}}
%-------------------------------------------------------------------------------
\input{spatial_discretization_shallowwater}

%-------------------------------------------------------------------------------
\subsubsection{Temporal discretization
\label{sec:temporal_discretization}}
%-------------------------------------------------------------------------------
\input{temporal_discretization}

%###############################################################################
\section{Methodology\label{sec:methodology}}
%###############################################################################
This section gives the methodology to be used in this research. As stated in
the introduction, both scalar and systems of hyperbolic PDEs are to be
considered. However, for brevity, this section gives only the scalar
methodology, since the methodology is very similar for systems. As stated in the
introduction, the FCT algorithm combines a low-order scheme and a high-order
scheme.  Thus this section is organized as follows.  Section
\ref{sec:low_order_scheme} gives the low-order scheme, Section
\ref{sec:high_order_scheme} gives the high-order scheme, and Section
\ref{sec:fct_scheme} gives the FCT scheme that blends the two schemes via the
FCT algorithm.
%===============================================================================
\subsection{Low-Order Scheme\label{sec:low_order_scheme}}
%===============================================================================
\input{low_order_scheme}

%===============================================================================
\subsection{High-Order Scheme\label{sec:high_order_scheme}}
%===============================================================================
\input{high_order_scheme}

%===============================================================================
\subsection{FCT Scheme\label{sec:fct_scheme}}
%===============================================================================
\input{fct_scheme}

%###############################################################################
\section{Preliminary Results\label{sec:results}}
%###############################################################################
\input{results}

%###############################################################################
\section{Research Goals\label{sec:goals}}
%###############################################################################
\input{goals}

%###############################################################################
\section{Conclusions\label{sec:conclusions}}
%###############################################################################
\input{conclusions}

%###############################################################################
\bibliographystyle{plain}
\bibliography{\refdir/references}
%###############################################################################

\end{document}
