\chapter*{ACKNOWLEDGEMENTS}
% Needs to be set to part, so the TOC doesnt add 'CHAPTER ' prefix in the TOC.
\addcontentsline{toc}{chapter}{ACKNOWLEDGEMENTS}  

\indent
First and foremost, I would like to thank my advisor, Dr. Jean Ragusa,
for his years of guidance, wisdom, patience, and expertise. I would also like to
thank Dr. Marco Delchini for his time, effort, and
knowledge in the development of methods for the shallow water equations.

I would like to thank Drs. Jean-Luc Guermond and Bojan Popov for their
time and expertise in entropy-based artificial dissipation and
conservation law methodology. Their recent work on discrete maximum principle-
preserving and invariant domain methods was the foundation of this dissertation.

I would like to thank all of those who have contributed to the
development of the \texttt{deal.II} finite element library, which has been
a tremendous help in the implementation of the methods given in this
dissertation. I would especially like to thank Drs. Wolfgang Bangerth
and Bruno Turcksin, who have quickly answered many questions I had regarding
the use of \texttt{deal.II}.

I would like to thank those who have contributed to the development
of FCT methods over the years, whose works were essential in the development
of the methodology used in this research. I would like to thank Dr. Dmitri Kuzmin
for his responses in my questions about FCT.

I would like to thank the the U.S. Department of Energy for providing
funding for this reasearch through the Nuclear Energy University
Programs (NEUP) fellowship. I would also like to thank Dr. Richard
Martineau of Idaho National Laboratory for providing funding of
the last two semesters of research.

Lastly, I would like to thank my friends and family for their love and support.

\pagebreak{}
